\documentclass{article}



\usepackage{setspace}
\usepackage[letterpaper]{geometry}
\setstretch{0.7}
\pagestyle{empty}
\geometry{verbose,tmargin=0.3in,bmargin=0.10in,lmargin=0.4in,rmargin=0.4in,headheight=0in,headsep=0in,footskip=0.3in}

% #1: Company #2: Date range #3: title #4:  Description
\newcommand{\work}[4]{
#3\\*
\indent\indent\small\makebox[2.20in][l]{#1} #2\footnotesize\\[.75em]
\makebox[0.15in][l]{}
\begin{minipage}[t]{7.00in}\footnotesize\itemsep0pt{#4}\end{minipage}
\\
\\
\normalsize
}


% #1: Company #2: Date range #3: title #4:  Description
\newcommand{\workold}[4]{
#3\\*
\indent\indent\small\makebox[2.20in][l]{#1} #2\footnotesize\\[.75em]

\normalsize
}

\newcommand{\skills}[1]{
\heading{Skills}
\makebox[0.25in][l]{}
\begin{minipage}[t]{7.00in}\small{#1}\end{minipage}
\\
}

\newcommand{\vol}[1]{
\heading{Volunteering}
\makebox[0.25in][l]{}
\begin{minipage}[t]{7.00in}\small{#1}\end{minipage}
\\
}

\newcommand{\heading}[1]{
\noindent\textbf{#1}
\\
}

\newcommand{\address}[1]{
\hfill{}\begin{minipage}[t]{2.00in}#1\end{minipage}
\\
}

\newcommand{\Objective}[1]{
\noindent\textbf{Objective}\\
 \indent\small #1\normalsize
\\
}


\begin{document}
\address{\textbf{Sean Head}\\
 408.372.7263\\
 headsean@gmail.com}

\Objective{I am searching for a technical position in systems
engineering that will give me the opportunity to practice and
expand my knowledge base and skill set. Positions within this scope
that are outside my specific experience particularly interest me as
they would allow me to learn new skills and concepts. }

\heading{Work Experience}

\work{Corona Labs Inc}{2008--2015, 2015-present}{Senior Systems Engineer, Director of Engineering}{
    \begin{itemize} \itemsep0em
        \item Guided Engineering team through acquisition by Perk.com.
        \item Worked with Product Design and Developer Relations teams to plan
        and set engineering pace and goals.
        \item Acted as technical liaison between Engineering and expanded international
        QA/support.
        \item Architected transition for back-end API's from a monolithic XML-RPC
        system to REST-based microservices (Laravel/Docker on AWS).
        \item Served as sole Systems Administrator for all internal and public facing
        services.
        \item Designed, implemented, and maintained application build queuing system
        (patent pending).
        \item Developed testing infrastructure for mobile applications in conjunction
        with a continuous integration system (Jenkins).
        \item Designed, implemented, and maintained a high volume mobile analytics system. Used Hadoop and HBase for data storage and analysis.
        \item Maintained internal application build cluster running on OS X, Windows 7, and Ubuntu Linux.
        \item Served as primary internal developer support for non core product issues (scripting, networking SME).
    \end{itemize}\itemsep1em
}

\work{Head Networks}{2006--2008}{Network Consultant/Owner}{
    \begin{itemize}\itemsep0em
        \item Designed and managed a multi-building campus-wide LAN including support
        servers (Windows 2003, Linux, VMware).
        \item Maintained a wide range of network switches and other devices from multiple vendors (Cisco, HP, Netgear, PFsense).
    \end{itemize}
}

\work{Pacific Custom Installations}{2004--2006}{Partner}{
    \begin{itemize}\itemsep0em
        \item Organized job site time tables and worked as a project manager with clients and general contractors.
        \item Worked with my partner designing, integrating, and automating Audio/Video systems integration.
\end{itemize}
}

\work{Terracom (ISP); Kigali, Rwanda}{2004}{Network/Telecommunications Consultant}{
    \begin{itemize}\itemsep0em
        \item Researched, planned and supervised the installation of the company's
        first passive optical network run. Including interfacing with government
        liaisons to plan fiber routes and initial deployment sites.
        \item Planned and configured caching web proxy system optimized for satellite
        latency.
        \item Taught a class for the NOC Team on network design and capacity planning. Used curriculum of my own design.
        \item Instructed physical plant team on usage and maintenance of fiber splicing tooling.
    \end{itemize}
}

\work{Digital Putty (ISP)}{2003--2004}{Wireless Network Engineer}{
    \begin{itemize}\itemsep0em
        \item Led projects to deploy additional tower locations, increasing
        the service area to 12 locations. With several links stretching
        20mi.
    \end{itemize}
}

\workold{Cyber Manor}{2002--2003}{Information Technology Administrator}{

}

\workold{Real-Wireless (ISP)}{2001--2003}{Information Technology Administrator}{

}

\workold{Physicianaccess.com}{1998--2002}{Network Administrator}{

}

\vol{
    \begin{itemize}\itemsep0em\footnotesize
        \item Drove to New Orleans after Katrina. Participated in temporary wireless backhaul buildout for EOCs and food distribution centers. Three months deployed time.
        \item Capactiy planning/design work on backup power generation system for a hospital in rural Ethiopia. Three weeks deployed time.
    \end{itemize}
}



\skills{
    \begin{itemize}\itemsep0em\footnotesize
        \item Windows and OS X desktop/server support
        \item Networking protocols (TCP, UDP, NTP, CIFS, NFS, HTTP, etc)
        \item Linux server support (Debian, Ubuntu, Puppet, Apache)
        \item Experienced in x86 hardware; including but not limited to system debugging,
        RAID subsystems, I/O planning
        \item Scripting languages: PHP, Lua, Bash, Puppet's Ruby DSL, Windows batch files
        \item Experience with storage networking (iSCSI, NFS, Fibre Channel)
        \item Experienced in wireless networking, in both a WAN and LAN setting
        \item Ethernet switching/LAN planning and configuration
        \item Cable installation; Ethernet, A/V, telecom, Single and Multi-mode fiber
        \item FCC licensed amateur radio operator (K6ZHS)
    \end{itemize}
}
\end{document}
